{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-22 thesis/tm.tex
tweak the position of tm abstraction verifs table, in the wake of new latex layout from the previous commit's paragraph
data-race

\begin{table}[t]

@@

		Tested with STM semantics, as both lock implementations include a retry loop.}

@@

\begin{itemize}
	\item An approach for model checkers to emulate strongly-atomic HTM
		by treating transactions as globally-uninterruptible atomic sections
		and injecting failure without simulating rollback
		(\cref{sec:tm-design-failure})
		and applying conventional data race analysis with all transactions treated as a global lock
		(\cref{sec:tm-design-locks}),
		plus an extension to also emulate weakly-atomic STM systems
		by relaxing the above atomicity to apply to other transactions only
		(\cref{sec:tm-weak-atomicity}),
		each section with a corresponding soundness proof of equivalence to existing systems' semantics.
	\item An implementation of both forms of transactional memory in Landslide,
		with further options to configure the variety of abort codes injected
		(\cref{sec:tm-implementation}).
	\item A suite of transactional benchmark programs,
		designed to produce interesting state spaces of varying size, bugginess, and reducibility
		(\cref{sec:tm-eval-exp-setup}).
		This test suite is more appropriate for evaluating model checkers
		% get rekt STAMP :triumph:
		than prior work, which to date has focused on testing the raw performance of TM backend implementations,
		with little focus on the interactions of abort paths.
	\item Two previously-unknown bugs found in transactional programs from prior work
		(\cref{sec:tm-eval-bugs}).
	\item Retry set reduction,
		a new state space reduction algorithm
		(\cref{sec:tm-retrysets})
		which the evaluation shows identifies and skips equivalent interleavings
		compared to standard DPOR, even when transactional and abort paths are fully mutually conflicting
		(\cref{sec:tm-eval-retrysets}).
	\item Demonstration of two further heuristic reduction strategies on HTM programs,
		abort code reduction (\cref{sec:tm-eval-stm})
		and abstraction reduction (\cref{sec:tm-abstraction})
		which rely on human intuition to ensure their soundness
		to tackle even larger state spaces still.
	\item Verifications of \Cref{fig:htm-fixed}'s atomicity protocol %(with retry set reduction)
		and the {\tt lock}({\tt mutex}) transactional lock %(with abort code reduction)
		up to 2 threads, 4 iterations and 4 threads, 1 iteration for each
		(\cref{sec:tm-verif}).
		%$(K,N)$=$(2,4)$ and $(4,1)$ for each.
		% verified htm atomicity protocol (htm2) and mutex (lock mutex) up to (2,4), (4,1)
\end{itemize}

>>>>

\begin{table}[hb!] % ugh... this placement directive... (be on same page as above figure)

@@

		Tested with STM semantics, as both lock implementations include a retry loop.
		% this above extra vspace necessary so that this table and fig6.9 get a page all to themselves,
		% without latex trying to sneak two lines of body prose in at the bottom or between them

@@

\begin{itemize}
	\item An approach for model checkers to emulate strongly-atomic HTM
		by treating transactions as globally-uninterruptible atomic sections
		and injecting failure without simulating rollback
		(\cref{sec:tm-design-failure})
		and applying conventional data-race analysis with all transactions treated as a global lock
		(\cref{sec:tm-design-locks}),
		plus an extension to also emulate weakly-atomic STM systems
		by relaxing the above atomicity to apply to other transactions only
		(\cref{sec:tm-weak-atomicity}),
		each section with a corresponding soundness proof of equivalence to existing systems' semantics.
	\item An implementation of both forms of transactional memory in Landslide,
		with further options to configure the variety of abort codes injected
		(\cref{sec:tm-implementation}).
	\item A suite of transactional benchmark programs,
		designed to produce interesting state spaces of varying size, bugginess, and reducibility
		(\cref{sec:tm-eval-exp-setup}).
		This test suite is more appropriate for evaluating model checkers
		% get rekt STAMP :triumph:
		than prior work, which to date has focused on testing the raw performance of TM backend implementations,
		with little focus on the interactions of abort paths.
	\item Two previously-unknown bugs found in transactional programs from prior work
		(\cref{sec:tm-eval-bugs}).
	\item Retry set reduction,
		a new state space reduction algorithm
		(\cref{sec:tm-retrysets})
		which the evaluation shows identifies and skips equivalent interleavings
		compared to standard DPOR, even when transactional and abort paths are fully mutually conflicting
		(\cref{sec:tm-eval-retrysets}).
	\item Demonstration of two further heuristic reduction strategies on HTM programs,
		abort code reduction (\cref{sec:tm-eval-stm})
		and abstraction reduction (\cref{sec:tm-abstraction})
		which rely on human intuition to ensure their soundness
		to tackle even larger state spaces still.
	\item Verifications of \Cref{fig:htm-fixed}'s atomicity protocol %(with retry set reduction)
		and the {\tt lock}({\tt mutex}) transactional lock %(with abort code reduction)
		up to 2 threads, 4 iterations and 4 threads, 1 iteration for each
		(\cref{sec:tm-verif}).
		%$(K,N)$=$(2,4)$ and $(4,1)$ for each.
		% verified htm atomicity protocol (htm2) and mutex (lock mutex) up to (2,4), (4,1)
\end{itemize}
